### 2016-12-10 paper/evaluation.tex
Updated plots with existing data
Updated subject section

We evaluated the characteristics of regression tests in open-source
development from a sample set of Java projects from
Github\Jbc{Remember to update the previous sentence after updating the
subject section}. We are interested in understanding the prevalence
of long test runs, the main sources of cost, and how often developers
explore parallelism to improve execution performance. More
specifically, we pose the following research questions:

@@

\newcommand{\RQB}{How often do developers use parallelism to improve
runtime performance?}

@@

The first research question addresses the distribution of subjects per
time cost. We are interested in identifying time-consuming test suites
to investigate further their characteristics (\eg, type of application
and bottlenecks from execution) \Jbc{do we have more arguments?}.  The
second research question addresses our interest in understanding if
developers are aware of parallelism features from testing frameworks
available out-of-the-box through build systems (\eg, run JUnit test
cases in parallel using Maven Surefire) and what setting are often
used. The third research question addresses the impact of parallelism
on the regression tests from our sample set. We are interested in
compare the execution performance with different parallel settings
(see Section~\ref{sec:modes}). The fourth research question addresses
the characteristics of regression tests from the previous experiment.
More specifically, we want to investigate if there is a relation
between the balance of test execution (\ie, how uniformly distributed
is the execution time across tests cases) and the usage of
computational resources (\ie, if tests are mostly CPU or IO intense)
that impacts the effectiveness of parallelization. Finally, the fifth
research question discusses the limitations and insights to overcome
the pitfalls of parallelization.

@@

\Jbc{Subject selection is currently OK but I will use another way (eg
Google BigQuery) to have access to more subjects.}We used the Github's
Search API~\cite{githubsearch} to fetch the top 1,000\footnote{The
Search API imposes the limit of 1,000 results regardless of the number
of matches from a search criteria.} Java projects with at least 100
stars. The number of stars indicates the interest and appreciation
from the community to a given project.
\Comment{(https://help.github.com/articles/about-stars/)} Although our
criteria is subjective, it is an approximation to find relevant
projects to conduct our study. We detected the build manager system
based on the files located in the root directory from the project in
the following precedence: Maven (\emph{pom.xml}), Gradle
(\emph{*.gradle} file), and Ant (\emph{build.xml}).\Jbc{Remember to
update the following values after updating the subject selection
approach.} From the 1,000 downloaded projects, we detected the build
system of \Fix{801} subjects (composed by 216 Maven, \Fix{564} Gradle,
and 21 Ant projects) and considered \Fix{164} Maven projects that we
were able to compile and test. We were unable to compile other
subjects because some of them are related to a particular platform
(\eg, Gradle implied Android), has unsolved dependencies (\eg, package
no longer available from the Maven public repository), or the build
process is based on user-defined tasks (\eg, Ant projects).

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.48\textwidth]{results/plots/piechart-timecost.pdf}
    \caption{\label{fig:piechart-time} Subjects grouped by elapsed time on test
    execution ($t$): short execution ($t < 1m$), medium execution ($1m \leq t <
    5m$), and long execution ($5m \leq t$).  \Fix{On the left side, results from
    sequential execution}; on the right side, results from default execution.}
\end{figure}

@@

\begin{figure}[h!]%
    \centering
    \Fix{scatter top, scatter bottom, legend r-value regression}
    \caption{\Fix{...use minutes instead of secs...}}%
    \label{fig:scatters}%
\end{figure}

>>>>

We evaluated the characteristics of regression tests in open-source
development from a sample set of Java projects from
Github\Jbc{Remember to update the previous sentence after updating the
subject section}. We are interested in understanding the prevalence
of long test runs, the main sources of cost, and how do developers
explore parallelism to improve execution performance. More
specifically, we pose the following research questions:

@@

\newcommand{\RQB}{\Fix{How often do developers use parallelism to improve
runtime performance?}}

@@

The first research question addresses the distribution of subjects per
time cost. We are interested in identifying time-consuming test suites
to investigate further their characteristics (\eg, type of application
and bottlenecks from execution).  The second research question
addresses our interest in understanding if developers are aware of
parallelism features from testing frameworks available out-of-the-box
through build systems (\eg, run JUnit test cases in parallel using
Maven Surefire) and what setting are often used. The third research
question addresses the impact of parallelism on the regression tests
from our sample set. We are interested in compare the execution
performance with different parallel settings (see
Section~\ref{sec:modes}). The fourth research question addresses the
characteristics of regression tests from the previous experiment.
More specifically, we want to investigate if there is a relation
between the balance of test execution (\ie, how uniformly distributed
is the execution time across tests cases) and the usage of
computational resources (\ie, if tests are mostly CPU or IO intense)
that impacts the effectiveness of parallelization. Finally, the fifth
research question discusses the limitations and insights to overcome
the pitfalls of parallelization.

@@

We used the Github's Search API~\cite{githubsearch} to fetch Java
projects based on Maven according to the following criteria: primary
language must be Java\footnote{In case of projects in multiple
languages, the Github API considers the predominant language as the
primary language.}; project with at least 100 stars; latest update on
(or after) January 1st, 2016; contains the string \emph{mvn} in the
\emph{README} file.  The number of stars indicates the interest and
appreciation from the community to a given project.
\Comment{(https://help.github.com/articles/about-stars/)} Although our
criteria is subjective, it is an approximation to find relevant
projects to conduct our study.  Figure~\ref{fig:subject-query}
illustrates the query.

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={stars,language,pushed,in},
    deletekeywords={true}
}
\begin{lstlisting}
https://api.github.com/search/repositories?q=
    stars:>=100+language:java+mvn%20in:readme+
    pushed:>=2016-01-01+sort:stars&page=1&per_page=100

\end{lstlisting}
\caption{\label{fig:subject-query} Query to the Github API for
    projects in Java with at least 100 stars, updated on January 1st,
    2016 (or later), and contains the string \emph{mvn} in the
    \emph{README} file.}
\end{figure}

As in December 12th, 2016, our search criteria returned 589 subjects.
From the 589 downloaded projects, we considered 312 projects that we
were able to compile and test. The others 277 could not be considered
because 39 were not Maven projects, 26 could not fetch all required
dependencies, 125 could not be compiled, and 87 could not execute the
tests. In addition, we first attempted to consider Gradle and Ant
projects but most of Gradle projects were related to Android apps and
libraries and adding support to Ant would require to parse the
\emph{build.xml} to identify the compilation and test commands since
the build process is based on user-defined tasks.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.48\textwidth]{plots/piechart-timecost.pdf}
    \caption{\label{fig:piechart-time} Subjects grouped by elapsed time on test
    execution ($t$): short execution ($t < 1m$), medium execution ($1m \leq t <
    5m$), and long execution ($5m \leq t$).  \Fix{On the left side, results from
    sequential execution}; on the right side, results from default execution.}
\end{figure}

@@

\begin{figure}[h!]%
    \centering
    \Comment{scatter top, scatter bottom, legend r-value regression}
    \caption{\Fix{...use minutes instead of secs...}}%
    \label{fig:scatters}%
\end{figure}
